Submission and Formatting Instructions for the Twenty-Eighth \\ International Conference on Machine Learning (ICML 2012)

### 2012-04-10 klein2012/main.tex
Correction d'une typo mentionnée dans les revues :
There is a strange sentence in line 491.
Correction simple suite à une remarque dans les revues :
Line 210: This warrants a reference to Abbeel & Ng 2004.

We see also note that if two policies share the same feature

@@

\begin{lemme}
\label{proposition1} Under assumptions \ref{assumption1} and
\ref{assumption2}, there exists a minimum $\theta^*$ of J. The
elements of the set $M^*=\{\theta^*\in\mathbb{R}^p:
J(\theta^*)=\inf_{\theta\in\mathbb{R}^p}J(\theta)\}$ satisfy
equation \eqref{existence.eq}.
\end{lemme}
\begin{proof}
Let the margin function $l$ be such that: $\forall s\in S, \forall
a\in A\backslash\pi_E(s), l(s,a)=c>l(s,\pi_E(s))=0$. Then $\forall
\theta\in\mathbb{R}^p,J(\theta)\geq\sum_{s\in
S}\nu_E(s)l(s,\pi_E(s))=0$. Let note $\hat{\theta}$ the vector
verifying \eqref{existence.eq}, it is clear that
$\|\hat{\theta}\|_2\neq0$. Let $x>0$ and
$\hat{\theta}_x$=$x\frac{\hat{\theta}}{\|\hat{\theta}\|_2}$, then
there exists $x$ such that $J(\hat{\theta}_x)=0$. Indeed, $\forall
s\in S$ :
\begin{align}
&J(\hat{\theta}_x)=0\\
\Leftrightarrow&\hat{\theta}_x^T\mu^E_{s\pi_E(s)}\geq\max_{a \in A\backslash\pi_E(s)}(\hat{\theta}_x^T\mu^E_{sa}+l(s,a))\\
\Leftrightarrow&x\geq\frac{c}{\hat{\theta}_1^T\mu^E_{s\pi_E(s)}-\max_{a \in A\backslash\pi_E(s)}\hat{\theta}_1^T\mu^E_{sa}}.
\end{align}
Then all the vectors $\hat{\theta}_x$ with $x\geq c_{max}=\max_{s\in
S}\frac{c}{\hat{\theta}_1^T\mu^E_{s\pi_E(s)}-\max_{a \in
A\backslash\pi_E(s)}\hat{\theta}_1^T\mu^E_{sa}}$ are such that:
$\inf_{\theta\in\mathbb{R}^p}J(\theta)\geq0=J(\hat{\theta}_x)\geq\inf_{\theta\in\mathbb{R}^p}J(\theta)$.
So $\hat{\theta}_x=\inf_{\theta\in\mathbb{R}^p}J(\theta)$ for $x\geq
c_{max}$. Finally let us show that the elements of the set
$M^*=\{\theta^*\in\mathbb{R}^p:
J(\theta^*)=\inf_{\theta\in\mathbb{R}^p}J(\theta)\}$ satisfy
equation \eqref{existence.eq}. As there exists $x$ such that
$J(\hat{\theta}_x)=0=\inf_{\theta\in\mathbb{R}^p}J(\theta)$, it
implies $J(\theta^*)=0$. So:
\begin{align}
&J(\theta^*)=0\\
\Leftrightarrow&\theta^{*T}\mu^E_{s\pi_E(s)}\geq\max_{a \in A\backslash\pi_E(s)}(\theta^{*T}\mu^E_{sa}+l(s,a))\\
\Rightarrow&\theta^{*T}\mu^E_{s\pi_E(s)}>\max_{a \in A\backslash\pi_E(s)}\theta^{*T}\mu^E_{sa}.
\end{align}
\end{proof}

>>>>

We see also note (as made explicit in \cite{abbeel2004apprenticeship}) that if two policies share the same feature

@@

\begin{lemme}
\label{proposition1} Under assumptions \ref{assumption1} and
\ref{assumption2}, there exists a minimum $\theta^*$ of J. The
elements of the set $M^*=\{\theta^*\in\mathbb{R}^p:
J(\theta^*)=\inf_{\theta\in\mathbb{R}^p}J(\theta)\}$ satisfy
equation \eqref{existence.eq}.
\end{lemme}
\begin{proof}
Let the margin function $l$ be such that: $\forall s\in S, \forall
a\in A\backslash\pi_E(s), l(s,a)=c>l(s,\pi_E(s))=0$. Then $\forall
\theta\in\mathbb{R}^p,J(\theta)\geq\sum_{s\in
S}\nu_E(s)l(s,\pi_E(s))=0$. Let $\hat{\theta}$ be the vector
verifying \eqref{existence.eq}, it is clear that
$\|\hat{\theta}\|_2\neq0$. Let $x>0$ and
$\hat{\theta}_x$=$x\frac{\hat{\theta}}{\|\hat{\theta}\|_2}$, then
there exists $x$ such that $J(\hat{\theta}_x)=0$. Indeed, $\forall
s\in S$ :
\begin{align}
&J(\hat{\theta}_x)=0\\
\Leftrightarrow&\hat{\theta}_x^T\mu^E_{s\pi_E(s)}\geq\max_{a \in A\backslash\pi_E(s)}(\hat{\theta}_x^T\mu^E_{sa}+l(s,a))\\
\Leftrightarrow&x\geq\frac{c}{\hat{\theta}_1^T\mu^E_{s\pi_E(s)}-\max_{a \in A\backslash\pi_E(s)}\hat{\theta}_1^T\mu^E_{sa}}.
\end{align}
Then all the vectors $\hat{\theta}_x$ with $x\geq c_{max}=\max_{s\in
S}\frac{c}{\hat{\theta}_1^T\mu^E_{s\pi_E(s)}-\max_{a \in
A\backslash\pi_E(s)}\hat{\theta}_1^T\mu^E_{sa}}$ are such that:
$\inf_{\theta\in\mathbb{R}^p}J(\theta)\geq0=J(\hat{\theta}_x)\geq\inf_{\theta\in\mathbb{R}^p}J(\theta)$.
So $\hat{\theta}_x=\inf_{\theta\in\mathbb{R}^p}J(\theta)$ for $x\geq
c_{max}$. Finally let us show that the elements of the set
$M^*=\{\theta^*\in\mathbb{R}^p:
J(\theta^*)=\inf_{\theta\in\mathbb{R}^p}J(\theta)\}$ satisfy
equation \eqref{existence.eq}. As there exists $x$ such that
$J(\hat{\theta}_x)=0=\inf_{\theta\in\mathbb{R}^p}J(\theta)$, it
implies $J(\theta^*)=0$. So:
\begin{align}
&J(\theta^*)=0\\
\Leftrightarrow&\theta^{*T}\mu^E_{s\pi_E(s)}\geq\max_{a \in A\backslash\pi_E(s)}(\theta^{*T}\mu^E_{sa}+l(s,a))\\
\Rightarrow&\theta^{*T}\mu^E_{s\pi_E(s)}>\max_{a \in A\backslash\pi_E(s)}\theta^{*T}\mu^E_{sa}.
\end{align}
\end{proof}
